---
title: "The RPackage project(Advanced R Programming)"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro

It is a very simple extension with some function for data analysis. 
These features were used during the Advanced Programming course in R and are mostly a demonstration of the knowledge gained, rather than a really useful and unique package.

## Installation 

```{r eval = FALSE}
devtools::install_github('https://github.com/TikshiKE/rpackassigment.git')
```

## Functionality

With this package you can work with raw .rds and .nc data.
Documentation for the functions is included.

# data.table 

```{r echo = TRUE, eval = FALSE}
#Load the package
library(rpackassigment)
#Temerature DDF
#Assign your filenames to some var
dir <- dir()
#Run the function to read this data and make small corrections(.rds)
dt <- read_and_combine_raw(dir('README_files'))
#Process your dataset to look properly with ddf_temp/precip
ddf <- ddf_temperature(dt)
#Calculate historical ddf and delta
final_dt <- ddf_calculations(final_temp)
```
# spatial data
```{r echo = TRUE, eval = FALSE}
#Load the package
library(rpackassigment)
#Read your spatial data(precipitaton, longitude and latitude)
aux <- read_spatial_data(dir)
```


